### 2021-07-10 src/paper/data/share_known_cases.tex
Improve the fit text. Add text to the data section of the share known cases and improve its figure.

>>>>

 \comment[id=K]{Stoye called this the ascertainment rate if I remember right. Maybe we should replace this everywhere}

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see \ref{sub:testing}
for a detailed description for how we model both rapid and PCR tests). For our model it
is important to have an estimate for the share of cases that is detected in the absence
of rapid tests. For this we rely on the
\href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} which relies on estimates
of the case fatality rate to estimate the number of total cases given the number of
deaths which are suspected to be perfectly observable. For 2020, we follow the reported
share of detected cases quite closely only interpolating the phase of November 2020 where
the testing policy was changed to give more priority to vulnerable groups. This lead to
more tests being done among older age groups which are also at the highest risk of dying
from CoViD-19 and an overestimation of the share of detected cases.
% After Christmas 2020
Similarly, the start of vaccinations after Christmas 2020 that were predominantly given
to nursing homes in the beginning and other vulnerable groups in spring, led to a
decrease in the number of deadly cases, leading to an increasing upward bias in the share
of detected cases. This is why we stop using the Dunkelzifferradar after Christmas.
Instead, we assume that that the share of detected cases would have stayed the same in
the absence of rapid tests. Thus, we also achieve in our model an increase in the share
of detected cases but this is driven from inside our model through increased testing and
follow-ups on positive rapid tests (see Section~\ref{subsec:results_share_known_cases}).
% Christmas and Easter
Lastly, we include reductions in the share known cases due to the two major holidays in
our simulation period, Christmas and Easter. During both holidays where many laboratories
do not process tests and most physicians' offices are closed, less PCR tests were done
leading to short and large drops in the share of known cases.

### 2021-07-10 src/paper/data/synthetic_population.tex
Improve the fit text. Add text to the data section of the share known cases and improve its figure.

% To cover that the Pfizer-BioNTech vaccine was later approved for younger age groups we
% put adolescents and children into two groups that follow after the general population.
% These groups do not become eligible within our simulation frame until June.

% \begin{figure}[ht]   % vaccinations by age group
%   \centering
%   \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
%   \caption{Simulated and Empirical Infections by Federal State}
%   \floatfoot{\noindent \textit{Note:} \textcolor{red}{To be written.}}
%   \label{fig:vaccinations_by_age_group}
% \end{figure}

\FloatBarrier
os

>>>>

To cover that the Pfizer-BioNTech vaccine was later approved for younger age groups we
put adolescents and children into two groups that follow after the general population.
These groups do not become eligible within our simulation frame until June.

\begin{figure}[ht]   % vaccinations by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
  \caption{Simulated and Empirical Infections by Federal State}
  \floatfoot{\noindent \textit{Note:} \textcolor{red}{To be written.}}
  \label{fig:vaccinations_by_age_group}
\end{figure}

\FloatBarrier

### 2021-07-10 src/paper/results/fit.tex
Improve the fit text. Add text to the data section of the share known cases and improve its figure.

% observed infections by federal state
Our model fit is also very good for the different German federal states. This holds not
only for the large states such as North Rhine-Westphalia or Bavaria but also for many
smaller states such as Hessen or Rhineland-Palatinate. This shows that the inclusion of
school vacations and relying on work reductions by \cite{Google2021} combined with the
assortativity of contacts on the county level is sufficient to represent many local
differences.  %
However, admittedly, there are several patterns that our model does not reproduce - for
example because we do not have cross-border travel nor population density. This explains
why our model produces too many infections for federal states such as Schleswig-Holstein
and why it predicts too few infections for states, such as Saxony, bordering high
incidence countries.\comment[id=K]{The Czech Republic had very high numbers in October
(max > 800) but they fell during Nov to 220 and then climbed again to 800 by Jan 12th so
that might be only part of the answer why Saxony had such high numbers.}
However, these missing features are irrelevant for our main conclusions.

>>>>

% observed infections by federal state
Our model fit is also very good for the different German federal states. This holds not
only for the large states such as North Rhine-Westphalia or Bavaria but also for many
smaller states such as Hessen or Rhineland-Palatinate. This shows that using school
vacations dates and work mobility reductions by \cite{Google2021} at the state level
combined with county and age group specific initial conditions (see
Section~\ref{sub:initial_conditions}) and county level assortativity of contacts is
sufficient to represent many local differences.  %
The fit is especially good given that our model does not aim to have a high local
resolution. For example we abstract from population density and cross-border travel. It
is, thus, unsurprising that there are states that we do not match well, such as very
thinly populated Mecklenburg-Vorpommern and Schleswig-Holstein or Saxony with its large
border to the Czech Republic that had a much higher incidence than
Germany.\comment[id=K]{The Czech Republic had very high numbers in October (max > 800)
but they fell during Nov to 220 and then climbed again to 800 by Jan 12th so that might
be only part of the answer why Saxony had such high numbers.}
